Lab 0006: Latent Dirichlet Allocation Applied to Revisions

### 2008-10-24 lda-paper.tex
previous work being worked on!

In the presence of fine grained changes and detailed changelogs

Developers topics the focus of develop

many changelogs how to sort by change type

interleaved changes relate similar changes

@@

Topic analysis of fine-grained revisions is important as often
revisions belonging to different topics are interleaved or even mixed
inside of commits. Using powerful topic analysis like Latent Semantic
Indexing (LSI) or Latent Dirichlet Allocation (LDA) one can seperate
these mixed signals into coherent topics. In this case a topic is a
set of tokens that are related to each other.

\section{Previous Work}
%   1. [ ] Intro to LDA
\subsection{Intro to LDA}

\subsection{LDA Work}
%      1. [ ] LDA itself
%      2. [ ] Maletic stuff
%      3. [ ] WCRE: Scott/Jim
%      4. [ ] WCRE: Bug LDA stuff
%      5. [ ] MSR: Challenge work
%      6. [ ] FCA work
%4. [ ] Methodology [0/9]

@@

>>>>

% In the presence of fine grained changes and detailed changelogs

% Developers topics the focus of develop

% many changelogs how to sort by change type

% interleaved changes relate similar changes

@@

Topic analysis of fine-grained revisions is important as often
revisions belonging to different topics are interleaved or even mixed
inside of commits.  Sometimes a single revision to a file contains
multiple bug fixes.  Using powerful topic analysis like Latent
Semantic Indexing (LSI) or Latent Dirichlet Allocation (LDA) one can
seperate these mixed signals into coherent topics. In this case a
topic is a set of tokens that are related to each other.

% We suppose this could help us to segment the revisions on the time
% line to discover parts of an iteration.

Topic analysis is useful because it can help us partition a project's
time-line into sub-iterations. By breaking apart an iteration we might
be able to extract the underlying software development process from
these artifacts.

In this paper we seek to explore how topics shift over time in
the source control repository of a project. We analyze commit
comments, and even source code per revision per each time window and
extract the topics in that time window. We expect that topic sets
will change over time and the change in topic sets indicate a change
in the focus of development.

\section{Previous Work}

\subsection{Intro to LDA}

XXX explain LDA \cite{944937}

\subsection{LDA Work}

Lukins, Kraft and Etzkorn~\cite{lukins2008} use LDA to help query for
finding related documents during bug localization tasks. They used LDA
to build a topic model and then query against it using sample
documents, the query would return relevant documentation.

LSI is related to LDA and has been used to identify topics in software
artifacts~\cite{1421013,1374321,10.1109/ICPC.2007.13,10.1109/ICPC.2006.17}.

Semantic Clustering \cite{1698774,1566153}

Linstead et al has proposed an author source code model using
LDA.\cite{10.1109/MSR.2007.20,NIPS2007637,1321709}

Grant et al. have used an alternative technique to LSI and LDA, they
used Independant Component Analysis to seperate topic signals from
software code.

Our technique differs in the sense we apply LDA temporally and we
apply to change comments.

%      1. [ ] LDA itself
%      2. [ ] Maletic stuff
%      3. [ ] WCRE: Scott/Jim
%      4. [ ] WCRE: Bug LDA stuff
%      5. [ ] MSR: Challenge work
%      6. [ ] FCA work
%4. [ ] Methodology [0/9]

@@

\bibliographystyle{alpha}
\bibliography{paper1}
